---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library("tidyverse")
library("sf")
library("leaflet")
```


## https://worldmap.harvard.edu/data/geonode:holyromanempire_551

```{r}
download.file("http://worldmap.harvard.edu/download/wfs/20109/zip?outputFormat=SHAPE-ZIP&service=WFS&request=GetFeature&format_options=charset%3AUTF-8&typename=geonode%3Aholyromanempire_551&version=1.0.0",
              destfile = "data/harvard-worldmap_holy-roman-empire.zip")
unzip(zipfile = "data/harvard-worldmap_holy-roman-empire.zip", exdir = "data/harvard-worldmap_holy-roman-empire")
```

This purports to be the Holy Roman Empire in 1034 CE and was obtained from https://worldmap.harvard.edu/data/geonode:holyromanempire_551

```{r}
harvard_worldmap_holyRomanEmpire <- read_sf("data/harvard-worldmap_holy-roman-empire")
harvard_worldmap_holyRomanEmpire %>%
  leaflet() %>%
  addTiles() %>%
  addPolygons()
```


https://worldmap.harvard.edu/data/geonode:holyromanempire_551

## Ancient World Mapping Center

The Ancient World Mapping Centre provides many different shapefiles, here are all the ones that look to me to be the Holy Roman Empire

```{r}
all_roman_shps <- c("Roman_Empire_Around_AD_75",
                    "roman_empire_60_bc_provinces",
                    "roman_empire_ad_117",
                    "roman_empire_ad_117_extent",
                    "roman_empire_ad_14_extent",
                    "roman_empire_ad_14_provinces",
                    "roman_empire_ad_200_extent",
                    "roman_empire_ad_200_provinces",
                    "roman_empire_ad_69_extent",
                    "roman_empire_ad_69_provinces",
                    "roman_empire_bc_60_extent"
                    )
get_shp_files <- function(layer.name) {
  all_files <- paste0(layer.name,
                      c(".dbf", ".prj", ".sbn", ".sbx", ".shp.xml", ".shx"))
  
  dir.create(file.path("data", layer.name))
  
  lapply(all_files,
         function(x) {
           download.file(
             url = paste0(
               "http://awmc.unc.edu/awmc/map_data/shapefiles/political_shading/",
               x
             ),
             destfile = file.path("data", layer.name, x)
           )
         })
  
}
invisible(lapply(all_roman_shps, function(x) get_shp_files(x)))
```


```{r}
empire_map <- function(layer.name){
  read_sf(file.path("data",layer.name)) %>%
    leaflet() %>%
    addTiles() %>%
    addPolygons()
}
```


roman_empire_60_bc_provinces

```{r}
empire_map("roman_empire_60_bc_provinces")
```

roman_empire_ad_117

```{r}
empire_map("roman_empire_ad_117")
```

roman_empire_ad_117_extent

```{r}
empire_map("roman_empire_ad_117_extent")
```

roman_empire_ad_14_extent

```{r}
empire_map("roman_empire_ad_14_extent")
```

roman_empire_ad_14_provinces

```{r}
empire_map("roman_empire_ad_14_provinces")
```

roman_empire_ad_200_extent

```{r}
empire_map("roman_empire_ad_200_extent")
```

roman_empire_ad_200_provinces

```{r}
empire_map("roman_empire_ad_200_provinces")
```

roman_empire_ad_69_extent

```{r}
empire_map("roman_empire_ad_69_extent")
```

roman_empire_ad_69_provinces

```{r}
empire_map("roman_empire_ad_69_provinces")
```

roman_empire_bc_60_extent

```{r}
empire_map("roman_empire_bc_60_extent")
```

